Neural Network Language Models for Automatic Speech Recognition

### 2018-12-12 paper/paper.tex
paper: Add external bibliography
paper: Improve citations

One of the first papers applying RNNs to Language Modeling was \cite{Milkolov10}. But since 2010, new RNN approaches have shown
improvement on the state-of-the-art. We examine these new architectures and
techniques for future work discussed in the Milkolov paper and analyze whether their
results indicate that improvements can be made on the baseline set by the paper.

@@

Unfortunately, Elman Network RNNs are not able to retain all the optimal
contextual in practice. The reasons for this are given by \cite{Bengio94},
but in summary the issue is that as we backpropagate through time the gradients
from states "further back" in the history start to get vanishingly small, meaning
that they can be easily disrupted by noise or newer information. This means
that the hidden layer doesn't retain long-term information since it is easily
disrupted by new information.

@@

\end{document}

>>>>

One of the first papers applying RNNs to Language Modeling was by Milkolov and others \cite{Milkolov10}.
But since 2010, new RNN approaches have shown improvement on the state-of-the-art.
We examine these new architectures and techniques for future work discussed in the
Milkolov paper and analyze whether their results indicate that improvements can be made
on the baseline set by the paper.

@@

Unfortunately, Elman Network RNNs are not able to retain all the optimal
contextual in practice. The reasons for this are given by Bengio\cite{Bengio94},
but in summary the issue is that as we backpropagate through time the gradients
from states "further back" in the history start to get vanishingly small, meaning
that they can be easily disrupted by noise or newer information. This means
that the hidden layer doesn't retain long-term information since it is easily
disrupted by new information.

@@

\bibliographystyle{plain}
\bibliography{bibliography.bib}
\end{document}
